---
header-includes:
  - \input{../tex/preamble}
documentclass: article
classoption:
  - a4paper
  - 12pt
geometry: margin=0.5cm
output:
  pdf_document:
    keep_tex: true
# script : arc-rope.Rmd
# author : Benjamin Rubinstein
# about  : Produces an Australian Research Council (ARC) style 
#          LaTeX publication list suitable for Research Opportunity and
#          Performance Evidence (ROPE). Such documents tend to list
#          publications from some lower-bouding year, in reverse chronological
#          order, structured by publication type. Typically appended to
#          publications is information on rankings, and citations.
#          By knitting this document into latex, the user can supplement output
#          as needed - e.g. with asterisks for relevant publications to a grant - 
#          but in theory this should take care of most of the work including
#          fetching and merging Google Scholar citations. (But note then to 
#          be careful about scholar rate limits.)
---

\newcounter{list}
\setcounter{list}{0}

\noindent \textbf{D8. Research Opportunity and Performance Evidence (ROPE)---Publication list}

\noindent Bibliometrics retrieved `r format(Sys.Date(), format="%b %d, %Y")`: citation counts from Google Scholar; A\*,A,B,C conference rankings from CORE2018; A\*,A,B,C journal rankings from ERA2010 and 2015 5-year impact factors from Thomson Reuters. 
Project ID and years funded are included for papers supported by an ARC grant. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("RefManageR")
BibOptions(check.entries=FALSE, first.inits=FALSE, max.names=50, bib.style="authortitle", style="latex")
bib <- ReadBib("../bib/citations.bib", check=FALSE)
source("bibliometrics.R")
cites <- ScholarCites("hMG_gR4AAAAJ")
sections <- list("Authored Books"="book",
                 "Book Chapters"="incollection",
                 "Refereed Journal Articles"="article",
                 "Fully-Refereed Conference Proceedings"="inproceedings",
                 "Other Publication Outputs"=list(
                   "Edited Proceedings"="proceedings", 
                   "Technical Reports"="techreport;misc"))
print.bibtype <- function(bib, btype) {
  cat("\\begin{enumerate}\n\\setcounter{enumi}{\\value{list}}\n\n")
  btype.split <- strsplit(btype, ";", fixed=T)[[1]]
  for (bt in btype.split) {
    ybib <- bib[bibtype = bt]
    for (yb in names(ybib)) {
      cat("\\item ")
      print(ybib[yb])
      if (any(yb == names(cites$pubs))) {
        citeCount <- cites$pubs[yb]
        if (citeCount > 0) {
          if (citeCount > 1) {
            cat(" \\textbf{(", cites$pubs[yb], " citations)}", sep="")
          } else {
            cat(" \\textbf{(", cites$pubs[yb], " citation)}", sep="")
          }
        }
      }
      cat("\n")
    }
  }
  cat("\n\\setcounter{list}{\\value{enumi}}\n\\end{enumerate}\n\n")
}
```

```{r books, echo=FALSE, comment="", results='asis'}
for (key in names(sections)) {
  cat("\n\n\\noindent\\textbf{", key, "}\n\n", sep="")
  if (is.list(sections[[key]])) {
    for (sub.ind in seq_along(sections[[key]])) {
      sub.head <- names(sections[[key]])[sub.ind]
      sub.key <- (sections[[key]])[[sub.ind]]
      cat("\n\n\\noindent\\textit{", sub.head, "}\n\n", sep="")
      print.bibtype(bib, sub.key)
    }
  } else {
    print.bibtype(bib, sections[[key]])
  }
}
```
